Wi-Fi Based Handwritten Signature Verification Using a Triplet Network

### 2019-10-01 191001_Paper_BDML_v2/bdml_v2.tex
paper_bdml: v2

%%
%% This is file `sample-sigconf.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigconf')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigconf.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf]{acmart}

@@

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\copyrightyear{2019}
\acmYear{2019}
\setcopyright{rightsretained}

%% These commands are for a PROCEEDINGS abstract or paper.
%\acmConference{SIGGRAPH '19 Talks}{July 28 - August 01, 2019}{Los Angeles, CA, USA}
%\acmDOI{10.1145/3306307.3328180}
%\acmISBN{978-1-4503-6317-4/19/07}
%\acmBooktitle{SIGGRAPH '19 Talks, 
%  July 28 - August 01, 2019, Los Angeles, CA}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Wi-Fi Based Handwritten Signature Verification Using a Triplet Network}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Young-Woong Kwon, Jooyoung Kim and Kar-Ann Toh}
%\authornote{Both authors contributed equally to this research.}
\affiliation{%
  \institution{School of Electrical and Electronic Engineering, Yonsei University}
  \streetaddress{50 Yonsei-ro}
  \city{Seodaemun-gu}
  \state{Seoul}
  \country{Korea}
  \postcode{03722}
}
%\email{herokwon@yonsei.ac.kr}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Y.Kwon, et al.}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
    In this paper, we propose a system for identity verification based on the handwritten signature signals captured by the Wi-Fi Channel State Information (CSI). 
    To facilitate a fast converging loss model, a kernel and the range space learning is initially adopted for mining the triplet inputs. 
    Subsequently, the triplet network is trained on a ConvNet structure using the mined triplet inputs. 
    Our experiments on an in-house Wi-Fi handwritten signature signal dataset show encouraging verification accuracy with faster training loss convergence comparing with the baseline triplet network and the Siamese network.
\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%

\begin{CCSXML}
    <ccs2012>
    <concept>
    <concept_id>10002978.10002991.10002992.10003479</concept_id>
    <concept_desc>Security and privacy~Biometrics</concept_desc>
    <concept_significance>500</concept_significance>
    </concept>
    <concept>   
    <concept_id>10010147.10010257.10010293.10010294</concept_id>
    <concept_desc>Computing methodologies~Neural networks</concept_desc>
    <concept_significance>500</concept_significance>
    </concept>
    </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Security and privacy~Biometrics}
\ccsdesc[500]{Computing methodologies~Neural networks}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{Wi-Fi signature signal, in-air handwritten signature verification, the Kernel and the Range space projection learning, triplet network.}

%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
%\begin{teaserfigure}
%  \includegraphics[width=\textwidth]{sampleteaser}
%  \caption{Seattle Mariners at Spring Training, 2010.}
%  \Description{Enjoying the baseball game from the third-base
%  seats. Ichiro Suzuki preparing to bat.}
%  \label{fig:teaser}
%\end{teaserfigure}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

@@

% Figure 1
\begin{figure*}[!ht]
    \includegraphics[width=\textwidth]{fig1_tcnn_kar_v6}
    \caption{An overview of the proposed system.} \label{fig1}
\end{figure*}

@@

\subsubsection{Network Structure and Parameter Settings:}
The multilayer feedforward network structure of KAR space learning is specified in Table~\ref{tab2}. With input data, size of 500$\times$30$\times$6, we set two network layers where the size of the each layer is 1024 and 16, respectively. Each layer is initialized with uniform distribution over [0, 1). We used $\sigma = {tan}^{-1}$ as the activation function following \cite{toh2018analytic}.
\begin{table}
    \caption{The network structure of KAR space learning.}
    \label{tab2}
    \begin{tabular}{ccc}
     \toprule
     Layer   & Size     & Activation \\
     \midrule
     Input   & 500$\times$30$\times$6 &            \\
     Fully-Connected 1 & 1$\times$1$\times$1024 & $\sigma = {tan}^{-1}$     \\
     Fully-Connected 2 & 1$\times$1$\times$16  & $\sigma = {tan}^{-1}$     \\
     Output  & 1$\times$1$\times$50   &            \\
     \bottomrule
    \end{tabular}
\end{table}

For the proposed system and the deep learning-based methods, we utilized the same ConvNet structure as specified in Table~\ref{tab1}. We trained the network starting with a learning rate of 0.00005 and a mini-batch size of 32. We optimized the loss by the Adam optimizer with $L2$ penalty of 0.0002 except for the output layer. The output layer was regularized using an $L2$ penalty of 0.0001. We initialized all network weights in the convolutional layers with normal distribution of zero-mean and standard deviation 0.01. The biases were also initialized with a normal distribution of 0.5 mean and standard deviation 0.01. For the triplet networks, the hyper-parameter regulating triplet loss is empirically set at 0.1. The training epochs were set at 1,500 for all three deep learning-based algorithms. For the linear methods such as LSE, SVM and TER, the input signals were resized to 500 $\times$ 30 by averaging along the subcarrier axes due to limitation of hardware memory. For the PCA-LSE, the input dimension was reduced to 40.
\begin{table}
    \caption{The structure of ConvNet model. For the convolution layer, the kernel is specified as (m$\times$m) sized filter $\times$ (\# of filters) / (\# of stride). For the max-pooling layer, (p$\times$p) sized pooling windows / \# of stride. The input sizes are denoted as rows $\times$ cols $\times$ \# of filters.}
    \label{tab1}
    \begin{tabular}{cccc}
     \toprule
     Layer     & Activation & Kernel / Stride & Input Size \\
     \midrule
     Conv 1    & ReLU       & (3$\times$3)$\times$64/1      & 500$\times$30$\times$6   \\
     MaxPool 1 &            & (2$\times$2)/1         & 500$\times$30$\times$64  \\
     Conv 2    & ReLU       & (3$\times$3)$\times$128/1     & 250$\times$15$\times$64 \\
     MaxPool 2 &            & (2$\times$2)/1         & 250$\times$15$\times$128 \\
     Conv 3    & ReLU       & (3$\times$3)$\times$256/1     & 125$\times$8$\times$128  \\
     MaxPool 3 &            & (2$\times$2)/1         & 125$\times$8$\times$256  \\
     Fully-Connected     & Sigmoid    & 16             & 63$\times$4$\times$256   \\
     $L2$ Norm  &            &                 & 1$\times$1$\times$16    \\
     Concat    &            &                 & 1$\times$1$\times$16    \\
     \bottomrule
    \end{tabular}
\end{table}

@@

Case I: Table~\ref{tab3} shows the average of EER performance from five runs of two-fold cross-validation tests under the optimal parameter setting. For 1-orientation inputs, SVM showed the best verification accuracy of 1.55\% EER. However, For 4-orientation inputs, all three deep learning-based methods showed better performance than hand-craft methods. This is, perhaps, due to the utilization of the original size (500$\times$30$\times$6) of the input data in the training stage for the deep learning based methods. The test EER performance of the proposed system is 19.35\%. The baseline triplet network without input mining showed slightly worse performance of 20.34\% EER. The Siamese network showed the worst verification performance of 23.53\% EER. The Siamese network is also a metric learning system, but differs from our system in that it receives two inputs and uses the contrastive loss function for training. 
\begin{table*}
    \caption{Performance benchmarking with respect to the best EER (\%) averaged from five runs of two-fold cross-validation tests.}
    \label{tab3}
    \begin{tabular}{cccl}
    \toprule
    \multirow{2}{*}{Methology} & \multicolumn{2}{c}{Best EER (\%)} & \multirow{2}{*}{Parameter setting} \\ \cline{2-3}           & 1-orientation & 4-orientation     &    \\
    \midrule
    LSE                                    & 35.40 & 48.44           &                           \\ 
    PCA-LSE                                & 16.87 & 30.79           & Reduced dimension=40        \\ 
    SVM(Linear)                            & 1.55 & 28.23            & c=1                        \\ 
    SVM(RBF)                               & 3.97 & 24.31            & c=1, $\gamma$=0.01/3000    \\ 
    TER-RM2                                & 13.29 & 35.84          & M=1,$\tau$=$\eta$=0.5      \\
    \midrule
    Siamese network                        & 16.86 & 23.53           & lr=0.00005                 \\ 
    Baseline triplet network               & 5.45 & 20.34           & lr=0.00005, $\alpha$=0.1   \\ 
    \textbf{Proposed system}               & \textbf{5.09} & \textbf{19.35}           & \textbf{lr=0.00005, $\alpha$=0.1}   \\
    \bottomrule
    \end{tabular}
\end{table*}

Case II: Fig.~\ref{fig2} (a) shows the ROC curves of the three compared deep learning-based methods. As shown in the figure, the proposed system clearly shows the largest Area Under Curve (AUC) among three compared methods. In Fig.\ref{fig2} (b) the training loss trends are plotted with respect to along the number of training iterations. Here, the proposed system shows the fastest training loss convergence followed by the baseline triplet network. In the figure, the y-axes of triplet network based methods and the Siamese network are normalized into $[0,1]$ since each loss function has different starting value. According to these observations, it can be concluded that the triplet input mining with KAR space learning improves not only the verification performance but also the training loss convergence speed.
% Figure 2,3
\begin{figure}[!ht]
    \begin{center}
    \subfigure[][ROC Curve]{
        \includegraphics[height=6.4cm]{fig_roc_v14.eps}}
    \subfigure[][Normalized training loss curve]{
        \includegraphics[height=6.4cm]{normalized_loss_curve_ma30_v2.eps}}
    \caption{(a) Receiver Operating Characteristic (ROC) Curves and 
    (b) normalized training loss trends}
    \label{fig2}
    \end{center}
 \end{figure}

\section{Conclusion}
In this paper, we proposed a system for identity verification based on the handwritten signature signals captured by the Wi-Fi Channel State Information (CSI). 
The kernel and the range space learning was adopted for mining the triplet inputs for fast loss convergence. 
Subsequently, the triplet network utilizing the ConvNet structure was trained with the mined triplet inputs based on the $L2$ distance comparison. 
Our experiments on an in-house Wi-Fi handwritten signature dataset showed not only an encouraging verification accuracy but also a faster training loss convergence compared with the baseline triplet network and the Siamese network.
%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
    This research was supported by Basic Science Research
    Program through the National Research Foundation of Korea
    (NRF) funded by the Ministry of Education, Science and
    Technology.

    \noindent(NRF-2018R1D1A1A09081956)
\end{acks}

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{bib_conf}
%\bibliography{sample-base}

\begin{table*}[]
    \caption{Authors' background}
    \centering
    \begin{tabular}{|l|l|l|l|}
    \hline
    Your Name        & Title          & Research Field      & Personal website \\ \hline
    Young-Woong Kwon & master student & Pattern Recognition & https://sites.google.com/site/machineintelligencelab/                \\ \hline
    Jooyoung Kim & Phd candidate & Pattern Recognition & https://sites.google.com/site/machineintelligencelab/                \\ \hline
    Kar-Ann Toh & full professor & Pattern Recognition & https://sites.google.com/site/machineintelligencelab/                \\ \hline
    \end{tabular}
\end{table*}

\end{document}
\endinput
%%
%% End of file `sample-sigconf.tex'.

>>>>

% This is "sig-alternate.tex" V2.1 April 2013
% This file should be compiled with V2.5 of "sig-alternate.cls" May 2012
%
% This example file demonstrates the use of the 'sig-alternate.cls'
% V2.5 LaTeX2e document class file. It is for those submitting
% articles to ACM Conference Proceedings WHO DO NOT WISH TO
% STRICTLY ADHERE TO THE SIGS (PUBS-BOARD-ENDORSED) STYLE.
% The 'sig-alternate.cls' file will produce a similar-looking,
% albeit, 'tighter' paper resulting in, invariably, fewer pages.
%
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V2.5) produces:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) NO page numbers
%
% as against the acm_proc_article-sp.cls file which
% DOES NOT produce 1) thru' 3) above.
%
% Using 'sig-alternate.cls' you have control, however, from within
% the source .tex file, over both the CopyrightYear
% (defaulted to 200X) and the ACM Copyright Data
% (defaulted to X-XXXXX-XX-X/XX/XX).
% e.g.
% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
%
% ---------------------------------------------------------------------------------------------------------------
% This .tex source is an example which *does* use
% the .bib file (from which the .bbl file % is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission, you *NEED* to 'insert'
% your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% ================= IF YOU HAVE QUESTIONS =======================
% Questions regarding the SIGS styles, SIGS policies and
% procedures, Conferences etc. should be sent to
% Adrienne Griscti (griscti@acm.org)
%
% Technical questions _only_ to
% Gerald Murray (murray@hq.acm.org)
% ===============================================================
%
% For tracking purposes - this is V2.0 - May 2012

\documentclass{sig-alternate-05-2015}

@@

\begin{document}

% Copyright
\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\doi{10.475/123_4}

% ISBN
\isbn{123-4567-24-567/08/06}

%Conference
\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}

\acmPrice{\$15.00}

%
% --- Author Metadata here ---
\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{Wi-Fi Based Handwritten Signature Verification Using a Triplet Network}
%\subtitle{[Extended Abstract]
%\titlenote{A full version of this paper is available as
%\textit{Author's Guide to Preparing ACM SIG Proceedings Using
%\LaTeX$2_\epsilon$\ and BibTeX} at
%\texttt{www.acm.org/eaddress.htm}}}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{1} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
%\alignauthor
Young-Woong Kwon, Jooyoung Kim and Kar-Ann Toh\\
       \affaddr{School of Electrical and Electronic Engineering}\\
       \affaddr{Yonsei University}\\
       \affaddr{Seoul, Korea}\\
       %\email{trovato@corporation.com}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
\date{1 October 2019}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\begin{abstract}
       In this paper, we propose a system for identity verification based on the handwritten signature signals captured by the Wi-Fi Channel State Information (CSI). 
       To facilitate a fast converging loss model, a kernel and the range space learning is initially adopted for mining the triplet inputs. 
       Subsequently, the triplet network is trained on a ConvNet structure using the mined triplet inputs. 
       Our experiments on an in-house Wi-Fi handwritten signature signal dataset show encouraging verification accuracy with faster training loss convergence comparing with the baseline triplet network and the Siamese network.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
       <ccs2012>
       <concept>
       <concept_id>10002978.10002991.10002992.10003479</concept_id>
       <concept_desc>Security and privacy~Biometrics</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
       <concept>   
       <concept_id>10010147.10010257.10010293.10010294</concept_id>
       <concept_desc>Computing methodologies~Neural networks</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
       </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Security and privacy~Biometrics}
\ccsdesc[500]{Computing methodologies~Neural networks}
%
% End generated code
%

%
%  Use this command to print the description
%
\printccsdesc

% We no longer use \terms command
%\terms{Theory}

%\keywords{ACM proceedings; \LaTeX; text tagging}
\keywords{Wi-Fi signature signal; in-air handwritten signature verification; the Kernel and the Range space projection learning; triplet network}

@@

% Figure 1
\begin{figure*}%[!ht]
\centering
    \includegraphics[width=\textwidth]{fig1_tcnn_kar_v6}
    \caption{An overview of the proposed system.} \label{fig1}
\end{figure*}

@@

\subsubsection{Network Structure and Parameter Settings:}
The multilayer feedforward network structure of KAR space learning is specified in Table~\ref{tab2}. With input data, size of 500$\times$30$\times$6, we set two network layers where the size of the each layer is 1024 and 16, respectively. Each layer is initialized with uniform distribution over [0, 1). We used $\sigma = {tan}^{-1}$ as the activation function following \cite{toh2018analytic}.
\begin{table}
\centering
    \caption{The network structure of KAR space learning.}
    \label{tab2}
    \begin{tabular}{|c|c|c|} \hline
     Layer   & Size     & Activation \\ \hline
     Input   & 500$\times$30$\times$6 &            \\ \hline
     Fully-Connected 1 & 1$\times$1$\times$1024 & $\sigma = {tan}^{-1}$     \\ \hline
     Fully-Connected 2 & 1$\times$1$\times$16  & $\sigma = {tan}^{-1}$     \\ \hline
     Output  & 1$\times$1$\times$50   &            \\\hline
    \end{tabular}
\end{table}

For the proposed system and the deep learning-based methods, we utilized the same ConvNet structure as specified in Table~\ref{tab1}. We trained the network starting with a learning rate of 0.00005 and a mini-batch size of 32. We optimized the loss by the Adam optimizer with $L2$ penalty of 0.0002 except for the output layer. The output layer was regularized using an $L2$ penalty of 0.0001. We initialized all network weights in the convolutional layers with normal distribution of zero-mean and standard deviation 0.01. The biases were also initialized with a normal distribution of 0.5 mean and standard deviation 0.01. For the triplet networks, the hyper-parameter regulating triplet loss is empirically set at 0.1. The training epochs were set at 1,500 for all three deep learning-based algorithms. For the linear methods such as LSE, SVM and TER, the input signals were resized to 500 $\times$ 30 by averaging along the subcarrier axes due to limitation of hardware memory. For the PCA-LSE, the input dimension was reduced to 40.
\begin{table}
\centering
    \caption{The structure of ConvNet model. For the convolution layer, the kernel is specified as (m$\times$m) sized filter $\times$ (\# of filters) / (\# of stride). For the max-pooling layer, (p$\times$p) sized pooling windows / \# of stride. The input sizes are denoted as rows $\times$ cols $\times$ \# of filters.}
    \label{tab1}
    \begin{tabular}{|c|c|c|c|} \hline
     Layer     & Activation & Kernel / Stride & Input Size \\ \hline
     Conv 1    & ReLU       & (3$\times$3)$\times$64/1      & 500$\times$30$\times$6   \\ \hline
     MaxPool 1 &            & (2$\times$2)/1         & 500$\times$30$\times$64  \\ \hline
     Conv 2    & ReLU       & (3$\times$3)$\times$128/1     & 250$\times$15$\times$64 \\ \hline
     MaxPool 2 &            & (2$\times$2)/1         & 250$\times$15$\times$128 \\ \hline
     Conv 3    & ReLU       & (3$\times$3)$\times$256/1     & 125$\times$8$\times$128  \\ \hline
     MaxPool 3 &            & (2$\times$2)/1         & 125$\times$8$\times$256  \\ \hline
     Fully-Connected     & Sigmoid    & 16             & 63$\times$4$\times$256   \\ \hline
     $L2$ Norm  &            &                 & 1$\times$1$\times$16    \\ \hline
     Concat    &            &                 & 1$\times$1$\times$16    \\ \hline
    \end{tabular}
\end{table}

@@

Case I: Table~\ref{tab3} shows the average of EER performance from five runs of two-fold cross-validation tests under the optimal parameter setting. For 1-orientation inputs, SVM showed the best verification accuracy of 1.55\% EER. However, For 4-orientation inputs, all three deep learning-based methods showed better performance than hand-craft methods. This is, perhaps, due to the utilization of the original size (500$\times$30$\times$6) of the input data in the training stage for the deep learning based methods. The test EER performance of the proposed system is 19.35\%. The baseline triplet network without input mining showed slightly worse performance of 20.34\% EER. The Siamese network showed the worst verification performance of 23.53\% EER. The Siamese network is also a metric learning system, but differs from our system in that it receives two inputs and uses the contrastive loss function for training. 
\begin{table*}
\centering
    \caption{Performance benchmarking with respect to the best EER (\%) averaged from five runs of two-fold cross-validation tests.}
    \label{tab3}
    \begin{tabular}{|c|c|c|l|} \hline
    \multirow{2}{*}{Methology} & \multicolumn{2}{|c|}{Best EER (\%)} & \multirow{2}{*}{Parameter setting} \\ \cline{2-3}           & 1-orientation & 4-orientation     &    \\ \hline
    LSE                                    & 35.40 & 48.44           &                           \\  \hline
    PCA-LSE                                & 16.87 & 30.79           & Reduced dimension=40        \\  \hline
    SVM(Linear)                            & 1.55 & 28.23            & c=1                        \\  \hline
    SVM(RBF)                               & 3.97 & 24.31            & c=1, $\gamma$=0.01/3000    \\  \hline
    TER-RM2                                & 13.29 & 35.84          & M=1,$\tau$=$\eta$=0.5      \\ \hline
    Siamese network                        & 16.86 & 23.53           & lr=0.00005                 \\  \hline
    Baseline triplet network               & 5.45 & 20.34           & lr=0.00005, $\alpha$=0.1   \\  \hline
    \textbf{Proposed system}               & \textbf{5.09} & \textbf{19.35}           & \textbf{lr=0.00005, $\alpha$=0.1}   \\ \hline
    \end{tabular}
\end{table*}

Case II: Fig.~\ref{fig2} (a) shows the ROC curves of the three compared deep learning-based methods. As shown in the figure, the proposed system clearly shows the largest Area Under Curve (AUC) among three compared methods. In Fig.\ref{fig2} (b) the training loss trends are plotted with respect to along the number of training iterations. Here, the proposed system shows the fastest training loss convergence followed by the baseline triplet network. In the figure, the y-axes of triplet network based methods and the Siamese network are normalized into $[0,1]$ since each loss function has different starting value. According to these observations, it can be concluded that the triplet input mining with KAR space learning improves not only the verification performance but also the training loss convergence speed.
% Figure 2,3
\begin{figure}%[!ht]
\centering
    \begin{center}
    \subfigure[][ROC Curve]{
        \includegraphics[height=6.4cm]{fig_roc_v14.eps}}
    \subfigure[][Normalized training loss curve]{
        \includegraphics[height=6.4cm]{normalized_loss_curve_ma30_v2.eps}}
    \caption{(a) Receiver Operating Characteristic (ROC) Curves and 
    (b) normalized training loss trends}
    \label{fig2}
    \end{center}
 \end{figure}

\section{Conclusion}
In this paper, we proposed a system for identity verification based on the handwritten signature signals captured by the Wi-Fi Channel State Information (CSI). 
The kernel and the range space learning was adopted for mining the triplet inputs for fast loss convergence. 
Subsequently, the triplet network utilizing the ConvNet structure was trained with the mined triplet inputs based on the $L2$ distance comparison. 
Our experiments on an in-house Wi-Fi handwritten signature dataset showed not only an encouraging verification accuracy but also a faster training loss convergence compared with the baseline triplet network and the Siamese network.
%\end{document}  % This is where a 'short' article might terminate

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
This research was supported by Basic Science Research
Program through the National Research Foundation of Korea
(NRF) funded by the Ministry of Education, Science and
Technology.

\noindent(NRF-2018R1D1A1A09081956)

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{bib_conf}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns

\end{document}
